Analysing Constraint Grammars with a SAT-solver

### 2016-03-08 paper/lrec/eval_futurework.tex
stuff

\begin{table}[]
\centering
\begin{tabular}{|p{2.80cm}|l|l|l|}

\hline
                   & \textsc{nld}  & \textsc{spa}lem  & \textsc{spa}nolem \\ \hline
\# rules           & 59            & 279       & 279     \\ \hline
\# readings        & 336           & 3905      & 1735    \\ \hline
\# true positives 
    \small{(internal + interaction)}
                   & 7 (6 + 1)     & n         & m ( + 25)   \\ \hline
\# false positives 
 \small{(internal + interaction)}
                   & 0        & n         & 5 +   \\ \hline

\clock{} with amb. 
           classes & ??s           & 5h 42m    &  ??m ?s  \\ \hline
\clock{} no amb. 
           classes & 10ish sec       & ?m ?s    & 15m 57s    \\ \hline

%\# variables: last rule & 33915         & 247153            &    \\ \hline

@@

The experiments revealed problems in all grammars. For the smaller
grammars, we were able to verify manually that the detected rules were
true positives.
%The results for the Finnish grammar are inconclusive, 
% For the Finnish grammar, we did not have time to
% investigate all of them, but among those we could, we found both true and false negatives.
We did not systematically check for false negatives in any of the
grammars, but we kept track of a number of known tricky cases; mostly
rules with negations and complex set operations.
%While this does not guarantee the lack of false negatives, it indicates some degree of reliability. 
As the tool matures and we add new features, a more in-depth analysis
will be needed.

@@

We include two versions of the Spanish grammar in table~\ref{table:res}: in column 2, we added the lemmas and word forms as described in Section~\ref{sec:realistic_readings}, and in column 3, we just added each word form and lemma as individual readings, allowed to combine with any other reading. 
This latter version ran much faster, but also resulted in 5 false positives, all for rules that require a lemma in a condition.
In addition, there were differences in the generated output; examples will be shown later in this section.

Again, we can classify the conflicts into internal and interaction. As an example of internal conflict, there are two rules that use \texttt{SET Cog = (np cog)}---the problem is that the tag \texttt{cog} does not exist in the Apertium dictionary for Spanish. As another example, four rules require a context word tagged as NP with explicit number, but the lexicon does not indicate any number with NPs. It is likely that this grammar has been written for an earlier version, where such tags have been in place.

>>>>

\begin{table}[]
\centering
\begin{tabular}{|p{2.8125cm}|l|l|l|}

\hline
                   & \textsc{nld}  & \textsc{spa}lem  & \textsc{spa}nolem \\ \hline
\# rules           & 59            & 279       & 279     \\ \hline
\# readings        & 336           & 3905      & 1735    \\ \hline
\# conflicts found \small{(internal + interaction)}
                   & 7 (6 + 1)     & 44 (20 + 24)     & 42 (17 + 25) \\ \hline
% \# false positives 
%  \small{(internal + interaction)}
%                    & 0             & 1 (1 + 0)       & 1 (1 + 0)  \\ \hline

\clock{} with amb. 
           classes & ??s           & 1h 46m    &  Xm Ys  \\ \hline

\clock{} no amb. 
           classes & XXs        & 44m       & 16m      \\ \hline

@@

The experiments revealed problems in all grammars. For the smaller
grammars, we were able to verify manually that the detected rules were
true positives.
%The results for the Finnish grammar are inconclusive, 
% For the Finnish grammar, we did not have time to
% investigate all of them, but among those we could, we found both true and false negatives.
We did not systematically check for false negatives in any of the
grammars, but we kept track of a number of known tricky cases; mostly
rules with negations and complex set operations.

%While this does not guarantee the lack of false negatives, it indicates some degree of reliability. 
As the tool matures and we add new features, a more in-depth analysis
will be needed.

@@

We include two versions of the Spanish grammar in table~\ref{table:res}: in column 2, we added the lemmas and word forms as described in Section~\ref{sec:realistic_readings}, and in column 3, we just added each word form and lemma as individual readings, allowed to combine with any other reading. 
This latter version ran much faster, but failed to detect two internal conflicts, both for rules that target a lemma in a condition.
More interesting observation, the first version failed to detect a true interaction conflict, because it marked the two rules as internal conflicts.
%In addition, there were differences in the generated output; examples will be shown later in this section.

As an example of internal conflict, there are two rules that use \texttt{SET Cog = (np cog)}---the problem is that the tag \texttt{cog} does not exist in the Apertium dictionary for Spanish. As another example, four rules require a context word tagged as NP with explicit number, but the lexicon does not indicate any number with NPs. It is likely that this grammar has been written for an earlier version, where such tags have been in place.
